---
title: "Real Data Analysis"
date: "2025-06-09"
author: "Yingying Fan, Jinchi Lv, Ao Sun and Yurou Wang"
output:
  prettydoc::html_pretty:
    theme: hpstr
    highlight: github
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Prediction_powered_ts <- function(X_m, y, tilde_y_m, p1, p2, obs_idx, test_idx, 
                                  strong_idx, h){
  Ti <- dim(tilde_y_m)[1]
  invisible(capture.output(tilde_y_fit <- VARX(zt = tilde_y_m, p=p2, xt = X_m[,strong_idx], m=0, include.mean = FALSE)))
  
  ar_est <- tilde_y_fit$Phi
  hat_y <- matrix(0,nrow = Ti, dim(tilde_y_m)[2])
  for(t in (p2+1):Ti){
    hat_y[t,] <- (diag(ncol(tilde_y_m)) - ar_est)%*%t(tilde_y_m[t,,drop = FALSE])
  }
  
  y_obs <- y[obs_idx]
  X_aug <- cbind(X_m[,strong_idx], hat_y) # only use highly correlated index
  X_aug_obs <- X_aug[obs_idx,]
  
  y_fit <- arima(y_obs, order = c(p1,0,0), xreg = X_aug_obs, include.mean = FALSE)
  
  X_future <- X_aug[test_idx,]

  
  predictions <- predict(y_fit, n.ahead = h, newxreg = X_future)$pred
  return(predictions)
}

Prediction_BJ <- function(X_m, y, tilde_y_m, p1, p2, obs_idx, test_idx, 
                                  strong_idx, h, alpha=0.05){
  #X_m \in R^{T \times p}: input exogenous predictors
  #y \in R^T: the target time series
  #tilde_y_m \in R^{T \times q}: the synthetic surrogate 
  #p1: the AR order for target ARX model
  #p2: the VAR order for synthetic surrogate 
  #obs_idx: the observed index for target data
  #test_idx: the unobserved index for target data, the union of obs_idx and test_idx is equal to the whole index
  #strong_idx: the important index for predictors
  
  
  Ti <- dim(tilde_y_m)[1]
  invisible(capture.output(tilde_y_fit <- VARX(zt = tilde_y_m, p=p2, xt = X_m[,strong_idx], m=0, include.mean = FALSE)))
  
  ar_est <- tilde_y_fit$Phi
  hat_y <- matrix(0,nrow = Ti, dim(tilde_y_m)[2])
  for(t in (p2+1):Ti){
    hat_y[t,] <- (diag(ncol(tilde_y_m)) - ar_est)%*%t(tilde_y_m[t,,drop = FALSE])
  }
  
  y_obs <- y[obs_idx]
  X_aug <- cbind(X_m[,strong_idx], hat_y) # only use highly correlated index
  X_aug_obs <- X_aug[obs_idx,]
  
  y_fit <- arima(y_obs, order = c(p1,0,0), xreg = X_aug_obs, include.mean = FALSE)
  
  var_e <- mean(y_fit$residuals^2)
  alpha_hat <- y_fit$coef[1:p1]
  I_q1 <- diag(p1-1)
  I_q1 <- cbind(I_q1, 0)
  A_hat <- rbind(alpha_hat, I_q1)
  X_future <- X_aug[test_idx,]
  predictions <- predict(y_fit, n.ahead = h, newxreg = X_future)$pred
  
  interval_m <- matrix(nrow = h, ncol = 2)
  var_h <- 0
  for(i in 1:h){
    res_var <- var_e*(A_hat%^%(i-1))[1,1]
    var_h <- res_var + var_h
    interval_m[i,1] <- predictions[i]-sqrt(var_h)*qnorm(alpha/2, lower.tail = FALSE)
    interval_m[i,2] <- predictions[i]+sqrt(var_h)*qnorm(alpha/2, lower.tail = FALSE)
  }
  return(list(predictions, interval = interval_m))
}


Bootstrap_powered_ts <- function(X_m, y, tilde_y_m, p1, p2, obs_idx, test_idx,
                                 strong_idx, h, alpha=0.05, B=500){
  #X_m \in R^{T \times p}: input exogenous predictors
  #y \in R^T: the target time series
  #tilde_y_m \in R^{T \times q}: the synthetic surrogate
  #p1: the AR order for target ARX model
  #p2: the VAR order for synthetic surrogate
  #obs_idx: the observed index for target data
  #test_idx: the unobserved index for target data, the union of obs_idx and test_idx is equal to the whole index
  #strong_idx: the important index for predictors


  Ti <- dim(tilde_y_m)[1]
  invisible(capture.output(tilde_y_fit <- VARX(zt = tilde_y_m, p=p2, xt = X_m[,strong_idx], m=0, include.mean = FALSE)))
  ar_est <- tilde_y_fit$Phi
  hat_y <- matrix(0,nrow = Ti, dim(tilde_y_m)[2])
  for(t in (p2+1):Ti){
    hat_y[t,] <- (diag(ncol(tilde_y_m)) - ar_est)%*%t(tilde_y_m[t,,drop = FALSE])
  }

  y_obs <- y[obs_idx]
  X_aug <- cbind(X_m[,strong_idx], hat_y) # only use highly correlated index
  X_aug_obs <- X_aug[obs_idx,]

  y_fit <- arima(y_obs, order = c(p1,0,0), xreg = X_aug_obs, include.mean = FALSE)

  residual_c <- y_fit$residuals
  residual_c <- residual_c[(p1+1):length(obs_idx)]
  #residual_c <- scale(residual_c, scale = FALSE) # demean

  X_future <- X_aug[test_idx,]
  predictions <- predict(y_fit, n.ahead = h, newxreg = X_future)$pred

  Boot_m <- matrix(nrow = B, ncol = h)
  for(b in 1:B){
    # bootstrap refit
    ## construct bootstrap dataset
    boot_error <- sample(residual_c, replace = TRUE, size = Ti)
    boot_y <- numeric(Ti)
    #boot_y[1:p1] <- boot_error[1:p1] # delete
    # regenerate ARX
    for (t in (p1 + 1):Ti) {
      ar_term <- sum(y_fit$coef[1:p1] * boot_y[(t - 1):(t - p1)])

      x_term <- sum(y_fit$coef[(p1+1): length(y_fit$coef)] * X_aug[t, ])

      boot_y[t] <- ar_term + x_term + boot_error[t]
    }

    # bootstrap estimation
    boot_y_fit <- arima(boot_y[obs_idx], order = c(p1,0,0), xreg = X_aug_obs, include.mean = FALSE)
    boot_predictions <- predict(boot_y_fit, n.ahead = h, newxreg = X_future)$pred

    # bootstrap error
    Boot_m[b,] <- boot_predictions - boot_y[test_idx]
   }


  interval_m <- matrix(nrow = h, ncol = 2)

  interval_m[,1] <- predictions + apply(Boot_m,2,quantile,alpha/2)
  interval_m[,2] <- predictions + apply(Boot_m,2,quantile,1-alpha/2)

  return(list(predictions, interval = interval_m))
}


Average_prediction <- function(y, H){
  pre_c <- rep(0, H)
  for(h in 1:H){
    pre_c[h] <- mean(y[length(y):(length(y)-h+1)])
  }
  return(pre_c)
} 



check_coverage <- function(pred_intervals, true_values) {
  coverage <- (true_values >= pred_intervals[1]) & (true_values <= pred_intervals[2])
  return(as.integer(coverage))
}
set.seed(1234)
library(dplyr)
library(forecast)
library(MTS)
library(lubridate)
library(expm)
```

## LLM-Powered Prediction with LDA Embedding 
```{r}
# read the LDA embedding dataset
setwd("/Users/sunao/Desktop/LLM-CPI code")
df <- read.csv('./meanTopicDistri_mergeCPI100_Unemployment_df19-23_20250301.csv')
colnames(df)
```

### Data preprocessing
```{r}
df_new <- df[,c(1,3,5:24)] 
df_new$unem <-df$全国城镇调查失业率... # unemployment rate
df_new$cpi <- df$cpi_lastmonth_100 # CPI index
df_new$time <- as.Date(df_new$time) # transfer variable ''time'' to Date type
df_new <- df_new %>%
  arrange(time) 

df_new <- df_new %>%
  mutate(
    month = format(time,"%Y-%m"),  # extract year and month
    day = day(time),                
    period = case_when(
      day <= 10 ~ "up",
      day <= 20 ~ "middle",
      TRUE ~ "down"
    )
  )


df_new <- df_new[,!names(df_new) %in% c("time")]

df_summary <- df_new %>%
  group_by(month, period) %>%
  summarise(across(everything(), mean, na.rm = TRUE))



y_m_list <- sort(unique(df_summary$month))
tilde_y_m <- matrix(ncol = 3, nrow = length(y_m_list))
for(i in 1:length(y_m_list)){
  res_ym <- y_m_list[i]
  tilde_y_m[i,] <- df_summary[df_summary$month == res_ym,]$pred_scoreInflation
}




X_m <- matrix(ncol = 20, nrow = length(y_m_list))
for(i in 1:length(y_m_list)){
  res_ym <- y_m_list[i]
  X_m[i,] <- apply(df_summary[df_summary$month == res_ym,4:23],2,mean)
}


y_df <- df_new %>%
  group_by(month) %>%
  summarise(y = mean(cpi))
y = y_df$y
y = y-100
y = scale(y)

y_df <- df_new %>%
  group_by(month) %>%
  summarise(y = mean(unem))
unem = y_df$y
unem = scale(unem)
```

### Data analysis

#### Variable Selection via correlation pursuit
```{r}
set.seed(1234)
EOD = 45 # we use first 45 data points to select the important variables
ar_fit <- auto.arima(y[1:EOD], max.q = 0, D = 0,seasonal = FALSE, allowmean = FALSE, allowdrift = FALSE)
ar_fit <- arima(y[1:EOD], order = c(ar_fit$arma[1],0,0), include.mean = FALSE)
aic_c <- NULL
for(i in 1:20){
  strong_idx <- order(abs(cov(ar_fit$residuals, X_m[1:EOD,])), decreasing = TRUE)[1:i]
  arx_fit <- arima(y[1:EOD,], order = c(ar_fit$arma[1],0,0), xreg = X_m[1:EOD,strong_idx], include.mean = FALSE)
  aic_c[i] <- EOD*log(mean((arx_fit$residuals)^2)+1)+ (2*(length(strong_idx)+1)*(length(strong_idx)+2))/(EOD - length(strong_idx)-2)
}
select_num <- which(diff(aic_c) <0)[1]+1
strong_idx <- order(abs(cov(ar_fit$residuals, X_m[1:EOD,])), decreasing = TRUE)[1:select_num]
strong_idx
```


#### Prediction
```{r}
set.seed(1234)
h_c <- seq(8,15,1)
Res_m <- matrix(nrow = length(h_c), ncol = 16)
for(k in 1:length(h_c)){
  h <- h_c[k]
  res_c <- NULL
  test_idx <- (length(y)-h+1):length(y)
  obs_idx <- setdiff(1:length(y), test_idx)
  
  # AR
  ar_fit <- auto.arima(y[obs_idx],max.q = 0, D = 0,seasonal = FALSE, allowmean = FALSE, allowdrift = FALSE)
  ar_fit <- arima(y[obs_idx], order = c(ar_fit$arma[1],0,0), include.mean = FALSE)
  ar_prediction <- predict(ar_fit, n.ahead = h)$pred
  res_c <- c(res_c, sqrt(mean((ar_prediction-y[test_idx])^2)))
  res_c <- c(res_c, mean(sign(ar_prediction) !=sign(y[test_idx])))
  
  #random walk
  mean_prediction <- rep(y[max(obs_idx)], length(test_idx))
  res_c <- c(res_c, sqrt(mean((mean_prediction-y[test_idx])^2)))
  res_c <- c(res_c, mean(sign(mean_prediction) !=sign(y[test_idx])))
  
  #Average 
  ave_prediction <- Average_prediction(y[obs_idx], length(test_idx))
  res_c <- c(res_c, sqrt(mean((ave_prediction-y[test_idx])^2)))
  res_c <- c(res_c, mean(sign(ave_prediction) !=sign(y[test_idx])))
  
  #AR + unemployment
  ar_unem_fit <- auto.arima(y[obs_idx], xreg = unem[obs_idx], max.q = 0, D = 0,seasonal = FALSE, allowmean = FALSE,      allowdrift = FALSE)
  ar_unem_fit <- arima(y[obs_idx], xreg = unem[obs_idx], order = c(ar_unem_fit$arma[1],0,0), include.mean = FALSE)
  ar_unem_prediction <- predict(ar_unem_fit, newxreg = unem[test_idx], n.ahead = h)$pred
  
  res_c <- c(res_c, sqrt(mean((ar_unem_prediction-y[test_idx])^2)))
  res_c <- c(res_c, mean(sign(ar_unem_prediction) !=sign(y[test_idx])))

   #AR + LDA embedding
  arx_fit <- arima(y[obs_idx], order = c(ar_fit$arma[1],0,0), xreg = X_m[obs_idx,strong_idx], include.mean = FALSE)
  arx_predictions <- predict(arx_fit, n.ahead = h, newxreg = X_m[test_idx,strong_idx])$pred
  
  res_c <- c(res_c, sqrt(mean((arx_predictions-y[test_idx])^2)))
  res_c <- c(res_c, mean(sign(arx_predictions) !=sign(y[test_idx])))
  
  # AR + unem + LDA embedding
  arx_unem_fit <- arima(y[obs_idx],order = c(2,0,0), xreg = cbind(X_m[obs_idx,strong_idx, drop=FALSE],unem[obs_idx]),    include.mean = FALSE)
  arx_unem_predictions <-predict(arx_unem_fit, n.ahead=h, newxreg=cbind(X_m[test_idx,strong_idx,drop=FALSE],  unem[test_idx]))$pred

  res_c <- c(res_c, sqrt(mean((arx_unem_predictions-y[test_idx])^2)))
  res_c <- c(res_c, mean(sign(arx_unem_predictions) !=sign(y[test_idx])))

  # LLM powered: lag term + LDA embedding
  p1=ar_fit$arma[1]
  p2=1
  
  powered_prediction <- Prediction_powered_ts(X_m, y, tilde_y_m, p1, p2, obs_idx, test_idx, strong_idx, h)

  res_c <- c(res_c, sqrt(mean((powered_prediction-y[test_idx])^2)))
  res_c <- c(res_c, mean(sign(powered_prediction) !=sign(y[test_idx])))
  
  # LLM powered: lag term + unem + LDA embedding
  powered_unem_prediction <- Prediction_powered_ts(cbind(X_m,unem), y, tilde_y_m, p1, p2, obs_idx, test_idx, 
                                              c(strong_idx,ncol(X_m)+1), h)

  
  res_c <- c(res_c, sqrt(mean((powered_unem_prediction-y[test_idx])^2)))
  res_c <- c(res_c, mean(sign(powered_unem_prediction) !=sign(y[test_idx])))
  Res_m[k,] <- res_c
}
```

```{r}
LDA_mse <- Res_m[,c(1,3,5,7,9,11,13,15)]
LDA_sign <- Res_m[,c(2,4,6,8,10,12,14,16)]
colnames(LDA_mse) <- c('AR','RW','AVE','ARX','LDA','LDA+X','LLM+LDA','LLM+LDA+X')
colnames(LDA_sign) <- c('AR','RW','AVE','ARX','LDA','LDA+X','LLM+LDA','LLM+LDA+X')
```




### Prediction interval with LDA embedding
```{r}
set.seed(1234)
h_c <- seq(8,15,1)

coverage_m <- matrix(0, nrow = length(h_c), ncol = 8)
len_m <- matrix(0, nrow = length(h_c), ncol = 8)

for(k in 1:length(h_c)){
  h <- h_c[k]
  
  test_idx <- (length(y)-h+1):length(y)
  obs_idx <- setdiff(1:length(y), test_idx)
  
  #AR 
  ar_fit <- Arima(y[obs_idx], order = c(ar_fit$arma[1],0,0),include.mean = FALSE)
  ar_predictions_fit <- forecast(ar_fit, h = length(test_idx))
  ar_interval <- cbind(ar_predictions_fit$lower[,2], ar_predictions_fit$upper[,2])
  len_m[k, 1] <- mean(as.numeric(ar_interval[,2] - ar_interval[,1]))
  coverage_m[k,1] <- mean(mapply(check_coverage, split(ar_interval, row(ar_interval)), y[test_idx]))
  
  #AR+unem
  ar_unem_fit <- Arima(y[obs_idx], order = c(ar_fit$arma[1],0,0), xreg = unem[obs_idx], include.mean = FALSE)
  ar_unem_predictions_fit <- forecast(ar_unem_fit, h = length(test_idx), xreg = unem[test_idx])
  ar_unem_interval <- cbind(ar_unem_predictions_fit$lower[,2], ar_unem_predictions_fit$upper[,2])
  len_m[k, 2] <- mean(as.numeric(ar_unem_interval[,2] - ar_interval[,1]))
  coverage_m[k,2] <- mean(mapply(check_coverage, split(ar_unem_interval, row(ar_unem_interval)), y[test_idx]))
  
 
  
  #AR+LDA embedding
  
  arx_lda_fit <- Arima(y[obs_idx], order = c(ar_fit$arma[1],0,0), xreg = X_m[obs_idx,strong_idx,drop = FALSE], include.mean = FALSE)
  arx_lda_predictions_fit <- forecast(arx_lda_fit, h = length(test_idx), xreg = X_m[test_idx,strong_idx,drop = FALSE])
  arx_lda_interval <- cbind(arx_lda_predictions_fit$lower[,2], arx_lda_predictions_fit$upper[,2])
  
  len_m[k,3] <- mean(arx_lda_interval[,2] - arx_lda_interval[,1])
  coverage_m[k,3] <- mean(mapply(check_coverage, split(arx_lda_interval, row(arx_lda_interval)), y[test_idx]))
  
  #AR+LDA + unem
   arx_lda_un_fit <- Arima(y[obs_idx], order = c(ar_fit$arma[1],0,0), xreg = cbind(X_m[obs_idx,strong_idx, drop=FALSE], unem[obs_idx]), include.mean = FALSE)
  arx_lda_un_predictions_fit <- forecast(arx_lda_un_fit, h = length(test_idx), xreg = cbind(X_m[test_idx,strong_idx,drop=FALSE], unem[test_idx]))
  arx_lda_un_interval <- cbind(arx_lda_un_predictions_fit$lower[,2], arx_lda_un_predictions_fit$upper[,2])
  
  len_m[k,4] <- mean(arx_lda_un_interval[,2] - arx_lda_un_interval[,1])
  coverage_m[k,4] <- mean(mapply(check_coverage, split(arx_lda_un_interval, row(arx_lda_un_interval)), y[test_idx]))
  
  #Powered+AR+LDA
  p1=ar_fit$arma[1]
  p2=1
  powered_lda_interval <- Prediction_BJ(X_m, y, tilde_y_m, p1, p2, obs_idx, test_idx, 
                                            strong_idx, h)$interval
  len_m[k,5] <- mean(powered_lda_interval[,2] - powered_lda_interval[,1])
  coverage_m[k,5] <- mean(mapply(check_coverage, split(powered_lda_interval, row(powered_lda_interval)), y[test_idx]))
  
  #Boot+AR+LDA
  boot_lda_interval <- Bootstrap_powered_ts(X_m, y, tilde_y_m, p1, p2, obs_idx, test_idx, strong_idx, h, B=2000)$interval
  
  len_m[k,6] <- mean(boot_lda_interval[,2] - boot_lda_interval[,1])
  coverage_m[k,6] <- mean(mapply(check_coverage, split(boot_lda_interval, row(boot_lda_interval)), y[test_idx]))
  
   #Powered+AR+LDA+unem

  powered_interval <- Prediction_BJ(cbind(X_m,unem), y, tilde_y_m, p1, p2, obs_idx, test_idx, 
                                    c(strong_idx,ncol(X_m)+1), h)$interval
  len_m[k,7] <- mean(powered_interval[,2] - powered_interval[,1])
  coverage_m[k,7] <- mean(mapply(check_coverage, split(powered_interval, row(powered_interval)), y[test_idx]))
  
  #Boot+AR+LDA+unem

  boot_interval <- Bootstrap_powered_ts(cbind(X_m,unem), y, tilde_y_m, p1, p2, obs_idx, test_idx, c(strong_idx,ncol(X_m)+1), h, B = 2000)$interval
   
  len_m[k,8] <- mean(boot_interval[,2] - boot_interval[,1])
  coverage_m[k,8] <- mean(mapply(check_coverage, split(boot_interval, row(boot_interval)), y[test_idx]))
}

```

```{r}
LDA_cov <- coverage_m
colnames(LDA_cov) <- c('AR','ARX','LDA', 'LDA+X', 'LLM+LDA(BJ)','LLM+LDA(Boot)','LLM+LDA(BJ)+X','LLM+LDA(Boot)+X')
LDA_len <- len_m
colnames(LDA_len) <- c('AR','ARX','LDA', 'LDA+X', 'LLM+LDA(BJ)','LLM+LDA(Boot)','LLM+LDA(BJ)+X','LLM+LDA(Boot)+X')
```

`

## LLM-Powered Prediction with transformer embedding
```{r}
setwd("/Users/sunao/Desktop/LLM-CPI code/")
df <- read.csv('./meanTopicDistri_mergeCPI100_Unemployment_df19-23_20250301.csv')
df_trans <- read.csv('./meanVector_mergeCPI_df19-23_20250201.csv')
df <- df[order(df$time),]
df_trans <- df_trans[order(df_trans$time),]
```


```{r}
df_new <- df_trans[,c(1,771, 3:770)]
df_new$time <- as.Date(df_new$time)
df_new <- df_new %>%
  arrange(time)

df_new <- df_new %>%
  mutate(
    month = format(time,"%Y-%m"),  
    day = day(time),                
    period = case_when(
      day <= 10 ~ "up",
      day <= 20 ~ "middle",
      TRUE ~ "down"
    )
  )


df_new <- df_new[,!names(df_new) %in% c("time")]

df_summary <- df_new %>%
  group_by(month, period) %>%
  summarise(across(everything(), mean, na.rm = TRUE))


X_m <- matrix(ncol = 20, nrow = length(y_m_list))
for(i in 1:length(y_m_list)){
  res_ym <- y_m_list[i]
  X_m[i,] <- apply(df_summary[df_summary$month == res_ym,4:23],2,mean)
}

X_m <- scale(X_m, center = FALSE)
```


#### Variable Selection via correlation pursuit
```{r}
set.seed(1234)
EOD = 45 # we use first 45 data points to select the important variables
ar_fit <- auto.arima(y[1:EOD], max.q = 0, D = 0,seasonal = FALSE, allowmean = FALSE, allowdrift = FALSE)
ar_fit <- arima(y[1:EOD], order = c(ar_fit$arma[1],0,0), include.mean = FALSE)
aic_c <- NULL
for(i in 1:20){
  strong_idx <- order(abs(cov(ar_fit$residuals, X_m[1:EOD,])), decreasing = TRUE)[1:i]
  arx_fit <- arima(y[1:EOD,], order = c(ar_fit$arma[1],0,0), xreg = X_m[1:EOD,strong_idx], include.mean = FALSE)
  aic_c[i] <- EOD*log(mean((arx_fit$residuals)^2)+1)+ (2*(length(strong_idx)+1)*(length(strong_idx)+2))/(EOD - length(strong_idx)-2)
}
select_num <- which(diff(aic_c) <0)[1]
strong_idx <- order(abs(cov(ar_fit$residuals, X_m[1:EOD,])), decreasing = TRUE)[1:select_num]
strong_idx
```



### Prediction
```{r}
set.seed(1234)
h_c <- seq(8,15,1)
Res_m <- matrix(nrow = length(h_c), ncol = 16)
for(k in 1:length(h_c)){
  h <- h_c[k]
  res_c <- NULL
  test_idx <- (length(y)-h+1):length(y)
  obs_idx <- setdiff(1:length(y), test_idx)
  
  # AR
  ar_fit <- auto.arima(y[obs_idx],max.q = 0, D = 0,seasonal = FALSE, allowmean = FALSE, allowdrift = FALSE)
  ar_fit <- arima(y[obs_idx], order = c(ar_fit$arma[1],0,0), include.mean = FALSE)
  ar_prediction <- predict(ar_fit, n.ahead = h)$pred
  ar_mse <- mean((ar_prediction-y[test_idx])^2)
  ar_sign <- mean(sign(ar_prediction) !=sign(y[test_idx]))
  res_c <- c(res_c, sqrt(mean((ar_prediction-y[test_idx])^2)))
  res_c <- c(res_c, mean(sign(ar_prediction) !=sign(y[test_idx])))
  
  #random walk
  mean_prediction <- rep(y[max(obs_idx)], length(test_idx))
  res_c <- c(res_c, sqrt(mean((mean_prediction-y[test_idx])^2)))
  res_c <- c(res_c, mean(sign(mean_prediction) !=sign(y[test_idx])))
  
  #Average 
  ave_prediction <- Average_prediction(y[obs_idx], length(test_idx))
  res_c <- c(res_c, sqrt(mean((ave_prediction-y[test_idx])^2)))
  res_c <- c(res_c, mean(sign(ave_prediction) !=sign(y[test_idx])))
  
  #AR + unemployment
  ar_unem_fit <- auto.arima(y[obs_idx], xreg = unem[obs_idx], max.q = 0, D = 0,seasonal = FALSE, allowmean = FALSE,      allowdrift = FALSE)
  ar_unem_fit <- arima(y[obs_idx], xreg = unem[obs_idx], order = c(ar_unem_fit$arma[1],0,0), include.mean = FALSE)
  ar_unem_prediction <- predict(ar_unem_fit, newxreg = unem[test_idx], n.ahead = h)$pred
  
  res_c <- c(res_c, sqrt(mean((ar_unem_prediction-y[test_idx])^2)/ar_mse))
  res_c <- c(res_c, mean(sign(ar_unem_prediction) !=sign(y[test_idx]))/ar_sign)

  # AR + TF embedding
  arx_fit <- arima(y[obs_idx], order = c(ar_fit$arma[1],0,0), xreg = X_m[obs_idx,strong_idx], include.mean = FALSE)
  arx_predictions <- predict(arx_fit, n.ahead = h, newxreg = X_m[test_idx,strong_idx])$pred
  
  res_c <- c(res_c, sqrt(mean((arx_predictions-y[test_idx])^2)/ar_mse))
  res_c <- c(res_c, mean(sign(arx_predictions) !=sign(y[test_idx]))/ar_sign)
  
  # AR + unem + TF embedding
  arx_unem_fit <- arima(y[obs_idx],order = c(2,0,0), xreg = cbind(X_m[obs_idx,strong_idx, drop=FALSE],unem[obs_idx]),    include.mean = FALSE)
  arx_unem_predictions <-predict(arx_unem_fit, n.ahead=h, newxreg=cbind(X_m[test_idx,strong_idx,drop=FALSE],  unem[test_idx]))$pred

  res_c <- c(res_c, sqrt(mean((arx_unem_predictions-y[test_idx])^2)/ar_mse))
  res_c <- c(res_c, mean(sign(arx_unem_predictions) !=sign(y[test_idx]))/ar_sign)

  # LLM powered: lag term + TF embedding
  p1=ar_fit$arma[1]
  p2=1
  
  powered_prediction <- Prediction_powered_ts(X_m, y, scale(tilde_y_m), p1, p2, obs_idx, test_idx, strong_idx, h)

  res_c <- c(res_c, sqrt(mean((powered_prediction-y[test_idx])^2)))
  res_c <- c(res_c, mean(sign(powered_prediction) !=sign(y[test_idx])))
  
  # LLM powered: lag term + unem + TF embedding
  powered_unem_prediction <- Prediction_powered_ts(cbind(X_m,unem), y, scale(tilde_y_m), p1, p2, obs_idx, test_idx, 
                                              c(strong_idx,ncol(X_m)+1), h)

  
  res_c <- c(res_c, sqrt(mean((powered_unem_prediction-y[test_idx])^2)))
  res_c <- c(res_c, mean(sign(powered_unem_prediction) !=sign(y[test_idx])))
  Res_m[k,] <- res_c
}
```

```{r}
TF_mse <- Res_m[,c(1,3,5,7,9,11,13,15)]
TF_sign <- Res_m[,c(2,4,6,8,10,12,14,16)]
colnames(TF_mse) <- c('AR','RW','AVE','ARX','TF','TF+X','LLM+TF', 'LLM+TF+X')
colnames(TF_sign) <- c('AR','RW','AVE','ARX','TF','TF+X', 'LLM+TF', 'LLM+TF+X')
```


### Prediction interval with transformer embedding
```{r}
set.seed(1234)
h_c <- seq(8,15,1)

coverage_m <- matrix(0, nrow = length(h_c), ncol = 8)
len_m <- matrix(0, nrow = length(h_c), ncol = 8)

for(k in 1:length(h_c)){
  h <- h_c[k]
  
  test_idx <- (length(y)-h+1):length(y)
  obs_idx <- setdiff(1:length(y), test_idx)
  
  #AR 
  ar_fit <- Arima(y[obs_idx], order = c(ar_fit$arma[1],0,0),include.mean = FALSE)
  ar_predictions_fit <- forecast(ar_fit, h = length(test_idx))
  ar_interval <- cbind(ar_predictions_fit$lower[,2], ar_predictions_fit$upper[,2])
  len_m[k, 1] <- mean(as.numeric(ar_interval[,2] - ar_interval[,1]))
  coverage_m[k,1] <- mean(mapply(check_coverage, split(ar_interval, row(ar_interval)), y[test_idx]))
  
  #AR+unem
  ar_unem_fit <- Arima(y[obs_idx], order = c(ar_fit$arma[1],0,0), xreg = unem[obs_idx], include.mean = FALSE)
  ar_unem_predictions_fit <- forecast(ar_unem_fit, h = length(test_idx), xreg = unem[test_idx])
  ar_unem_interval <- cbind(ar_unem_predictions_fit$lower[,2], ar_unem_predictions_fit$upper[,2])
  len_m[k, 2] <- mean(as.numeric(ar_unem_interval[,2] - ar_interval[,1]))
  coverage_m[k,2] <- mean(mapply(check_coverage, split(ar_unem_interval, row(ar_unem_interval)), y[test_idx]))
  
 
  
  #AR+LDA embedding
  
  arx_TF_fit <- Arima(y[obs_idx], order = c(ar_fit$arma[1],0,0), xreg = X_m[obs_idx,strong_idx,drop = FALSE], include.mean = FALSE)
  arx_TF_predictions_fit <- forecast(arx_TF_fit, h = length(test_idx), xreg = X_m[test_idx,strong_idx,drop = FALSE])
  arx_TF_interval <- cbind(arx_TF_predictions_fit$lower[,2], arx_TF_predictions_fit$upper[,2])
  
  len_m[k,3] <- mean(arx_TF_interval[,2] - arx_TF_interval[,1])
  coverage_m[k,3] <- mean(mapply(check_coverage, split(arx_TF_interval, row(arx_TF_interval)), y[test_idx]))
  
  #AR+TF + unem
  arx_TF_un_fit <- Arima(y[obs_idx], order = c(ar_fit$arma[1],0,0), xreg = cbind(X_m[obs_idx,strong_idx, drop=FALSE], unem[obs_idx]), include.mean = FALSE)
  arx_TF_un_predictions_fit <- forecast(arx_TF_un_fit, h = length(test_idx), xreg = cbind(X_m[test_idx,strong_idx,drop=FALSE], unem[test_idx]))
  arx_TF_un_interval <- cbind(arx_TF_un_predictions_fit$lower[,2], arx_TF_un_predictions_fit$upper[,2])
  
  len_m[k,4] <- mean(arx_TF_un_interval[,2] - arx_TF_un_interval[,1])
  coverage_m[k,4] <- mean(mapply(check_coverage, split(arx_TF_un_interval, row(arx_TF_un_interval)), y[test_idx]))
  
  #Powered+AR+TF
  p1=ar_fit$arma[1]
  p2=1
  powered_TF_interval <- Prediction_BJ(X_m, y, tilde_y_m, p1, p2, obs_idx, test_idx, 
                                            strong_idx, h)$interval
  len_m[k,5] <- mean(powered_TF_interval[,2] - powered_TF_interval[,1])
  coverage_m[k,5] <- mean(mapply(check_coverage, split(powered_TF_interval, row(powered_TF_interval)), y[test_idx]))
  
  #Boot+AR+TF
  boot_TF_interval <- Bootstrap_powered_ts(X_m, y, tilde_y_m, p1, p2, obs_idx, test_idx, 
                                        strong_idx, h)$interval
  
  len_m[k,6] <- mean(boot_TF_interval[,2] - boot_TF_interval[,1])
  coverage_m[k,6] <- mean(mapply(check_coverage, split(boot_TF_interval, row(boot_TF_interval)), y[test_idx]))
  
   #Powered+AR+TF+unem

  powered_interval <- Prediction_BJ(cbind(X_m,unem), y, tilde_y_m, p1, p2, obs_idx, test_idx, 
                                    c(strong_idx,ncol(X_m)+1), h)$interval
  len_m[k,7] <- mean(powered_interval[,2] - powered_interval[,1])
  coverage_m[k,7] <- mean(mapply(check_coverage, split(powered_interval, row(powered_interval)), y[test_idx]))
  
  #Boot+AR+TF+unem

  boot_interval <- Bootstrap_powered_ts(cbind(X_m,unem), y, tilde_y_m, p1, p2, obs_idx, test_idx, 
                                        c(strong_idx,ncol(X_m)+1), h)$interval
   
  len_m[k,8] <- mean(boot_interval[,2] - boot_interval[,1])
  coverage_m[k,8] <- mean(mapply(check_coverage, split(boot_interval, row(boot_interval)), y[test_idx]))
}

```


```{r}
TF_cov <- coverage_m
colnames(TF_cov) <- c('AR','ARX','TF', 'TF+X', 'LLM+TF(BJ)','LLM+TF(Boot)','LLM+TF(BJ)+X','LLM+TF(Boot)+X')
TF_len <- len_m
colnames(TF_len) <- c('AR','ARX','TF', 'TF+X', 'LLM+TF(BJ)','LLM+LDA(Boot)','LLM+TF(BJ)+X','LLM+TF(Boot)+X')
```


## Prediction results

### Results without unemployment rate 
```{r}
MSE_without_unem <- cbind(LDA_mse[,c(1,2,3,5,7)], TF_mse[,c(5,7),drop=FALSE])
MSE_without_unem <- MSE_without_unem[,c(1,2,3,4,6,5,7)]
rMSE_without_unem <- sweep(MSE_without_unem, 1, MSE_without_unem[,1,drop=FALSE], "/")
rMSE_without_unem <- cbind(h_c, rMSE_without_unem)
knitr::kable(rMSE_without_unem,col.names = c('H','AR','RW','AVE','LDA','TF','LLM+LDA','LLM+TF'), digits = 3, caption = 'rPMSE without unemployment rate')
colMeans(rMSE_without_unem)
```



```{r}
Sign_without_unem <- cbind(LDA_sign[,c(1,2,3,5,7)], TF_sign[,c(5,7),drop=FALSE])
Sign_without_unem <- Sign_without_unem[,c(1,2,3,4,6,5,7)]
rSign_without_unem <- sweep(Sign_without_unem, 1, Sign_without_unem[,1,drop=FALSE], "/")
rSign_without_unem <- cbind(h_c, rSign_without_unem)
knitr::kable(rSign_without_unem,col.names = c('H','AR','RW','AVE','LDA','TF','LLM+LDA', 'LLM+TF'), digits = 3, caption = 'rSign without unemployment rate')
colMeans(rSign_without_unem)
```

### Results with unemployment rate 
```{r}
MSE_with_unem <- cbind(LDA_mse[,c(4,2,3,6,8)], TF_mse[,c(6,8),drop=FALSE])
MSE_with_unem <- MSE_with_unem[,c(1,2,3,4,6,5,7)]
rMSE_with_unem <- sweep(MSE_with_unem, 1, MSE_with_unem[,1,drop=FALSE], "/")
rMSE_with_unem <- cbind(h_c, rMSE_with_unem)
knitr::kable(rMSE_with_unem,col.names = c('H','AR','RW','AVE','LDA','TF','LLM+LDA','LLM+TF'), digits = 3, caption = 'rPMSE with unemployment rate')
colMeans(rMSE_with_unem)
```


```{r}
Sign_with_unem <- cbind(LDA_sign[,c(4,2,3,6,8)], TF_sign[,c(6,8),drop=FALSE])
Sign_with_unem <- Sign_with_unem[,c(1,2,3,4,6,5,7)]
rSign_with_unem <- sweep(Sign_with_unem, 1, Sign_with_unem[,1,drop=FALSE], "/")
rSign_with_unem <- cbind(h_c, rSign_with_unem)
knitr::kable(rSign_with_unem,col.names = c('H','AR','RW','AVE','LDA','TF','LLM+LDA','LLM+TF'), digits = 3, caption = 'rSign with unemployment rate')
colMeans(rSign_with_unem)
```


## Inference results

### Results without unemployment rate 
```{r}
Cov_without_unem <- cbind(LDA_cov[,c(1,3,5,6)], TF_cov[,c(3,5,6)])
Cov_without_unem <- Cov_without_unem[,c(1,2,5,3,4,6,7)]
Cov_without_unem <- cbind(h_c, Cov_without_unem)
knitr::kable(Cov_without_unem, col.names = c('H','AR','LDA','TF','LLM+LDA(BJ)','LLM+LDA(Boot)','LLM+TF(BJ)','LLM+TF(Boot)'), digits = 3, caption = 'Coverage rate without unemployment rate')
```


```{r}
Len_without_unem <- cbind(LDA_len[,c(1,3,5,6)], TF_len[,c(3,5,6)])
Len_without_unem <- Len_without_unem[,c(1,2,5,3,4,6,7)]
Len_without_unem <- cbind(h_c, Len_without_unem)
knitr::kable(Len_without_unem, col.names = c('H','AR','LDA','TF','LLM+LDA(BJ)','LLM+LDA(Boot)','LLM+TF(BJ)','LLM+TF(Boot)'), digits = 3, caption = 'Interval length without unemployment rate')
```

### Results with unemployment rate 
```{r}
Cov_with_unem <- cbind(LDA_cov[,c(2,4,7,8)], TF_cov[,c(4,7,8)])
Cov_with_unem <- Cov_with_unem[,c(1,2,5,3,4,6,7)] 
Cov_with_unem <- cbind(h_c, Cov_with_unem)
knitr::kable(Cov_with_unem, col.names = c('H','AR','LDA','TF','LLM+LDA(BJ)','LLM+LDA(Boot)','LLM+TF(BJ)','LLM+TF(Boot)'), digits = 3, caption = 'Coverage rate with unemployment rate')
```

```{r}
Len_with_unem <- cbind(LDA_len[,c(2,4,7,8)], TF_len[,c(4,7,8)])
Len_with_unem <- Len_with_unem[,c(1,2,5,3,4,6,7)]
Len_with_unem <- cbind(h_c, Len_with_unem)
knitr::kable(Len_with_unem, col.names = c('H','AR','LDA','TF','LLM+LDA(BJ)','LLM+LDA(Boot)','LLM+TF(BJ)','LLM+TF(Boot)'), digits = 3, caption = 'Interval length with unemployment rate')
```


